Satellite Alignments in Galaxy Pairs

### 2016-06-10 paper/ms.tex
some more references

@@

>>>>

\citep{2012MNRAS.424...80P} Compare the kinematic structure of the MW
satellites against DM only simulation of high resolutions halos from
the Via Lactea and Aquarius projects.  Cannot find a similar kinematic
structure (i.e. the orbital poles of the MW satellites) in the
simulations.

@@

\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
spatial anisotropy the 11 brightest satellites. THe anisotropy is
quantified the reduced inertia tensor. Still the MW is more
anisotropic than all but one of the 24 halos. The analysis is not very
thorough and do not show the resulting distribution. Does not compare
the results of using DM information only.

\citep{2015ApJ...815...19P} argue that the result from
\citep{2016MNRAS.457.1931S} is a produc of using a metric that ignores
the radial position of the galaxies. They use the ELVIS suite to
compare the two analysis methods: reduced vs. full inertia tensor.

\citep{2016arXiv160501728S} Use the eagle simulation to study the
alignment of satellites with respect to the central galaxy. They find
a weak alignment. Around $20\%$ of the systems have a misalignment
angle larger than the value observed for the Milky Way. They do not
study DM only simulations and do not narrow down the signal to pairs.

\citep{2016arXiv160601516L} Using SDSS DR10 studied galaxy pairs. They find
that satellites tend to accumulate towards the companion galaxy. There
are up to $\sim 10\%$ more satellites in the space between the pair
than expected from an uniform distribution
